### 2018-04-25 README.Rmd
readme updated

Or you can install this compendium as an R package, ShortTermOccupations, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jmcascalheira/ShortTermOccupations")
```
### Licenses

@@

>>>>

This repository is organized as an R package using rrtools by Ben Marwick which can be installed from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/rrtools")
```

There are no actual R functions in this package - all the R code is in the Rmd file. I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.

To download the package source as you see it on GitHub, for offline browsing, use this line at the shell prompt (assuming you have Git installed on your computer):

```{r eval=FALSE}
git clone https://github.com/jmcascalheira/ShortTermOccupations.git
```

Once the download is complete, open the `ShortTermOccupations.Rproj` in RStudio to begin working with the package and compendium files.

The package has a number of dependencies on other R packages, and programs outside of R. Installing these can be time-consuming and complicated, so we've included a  packrat directory, which contains the source code for all the packages we depend on. If all works well, these will be installed on your computer when you open `ShortTermOccupations.Rproj` in RStudio.

### Licenses

@@

### Contact:

João Cascalheira, Post-Doc Researcher, ICArEHB
University of Algarve, Campus de Gambelas
8005-139 Faro PORTUGAL
e. jmcascalheira@ualg.pt  w. http://www.icarehb.com/cascalheira
